\bf{Inequality in non-cognitive skills: \\ a cross-cohort comparison}

### 2018-05-19 codes/R/slides/cohorts_tapes.Rnw
slides file

<<READ, cache=FALSE >>=
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/1_load.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/2_efa.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_mifa_invariance.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/3_mifa_final.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/4_scores_compare.R")
read_chunk("/Users/giacomomason/Documents/Projects/CohortStudies/codes/R/5_graphs.R")

@@

<<PREAMBLE>>=
@

@@

\date[NCDS]{NCDS 60 Years of Our Lives \\ \today}

@@

\begin{frame}
\frametitle{Harmonisation}
\framesubtitle{Choice of common items}
\centering
\resizebox{!}{4cm}{
<<ITEM_TEXT, dependson="MEANTABLE", results='asis'>>=
require(xtable)

table <- meantab
table <- table[,!names(meantab) %in% c("cats", "fac", "bcs.num", "mcs.num")] # drop if unneeded

@@

<<FA_INVARIANCE>>=
# estimate models of different levels of invariance
@

<<FA_FIT, dependson='FA_INVARIANCE'>>=
# assemble fit indices into matrices
@

<<FA_FINAL, dependson='FA_INVARIANCE'>>=
# select final model set
@

<<FA_FINAL_PARS, dependson='FA_FINAL'>>=
# get parameters of final model
@

<<CLEANUP, dependson='FA_FINAL'>>=
@

<<FA_SCORES, dependson='FA_FINAL'>>=
# produce scores for different models
@

<<FA_SCORES_MERGE, dependson='LOAD_DATA'>>=
# merge scores with other data
@

<<FA_SCORES_COMPARE, dependson='FA_SCORES'>>=
# assemble and compare scores across different models
@

<<FA_SCORES_SELECT, dependson='FA_SCORES_COMPARE'>>=
# select model to use for inequality analysis
@

@@

\begin{frame}
\frametitle{Measurement Invariance}\label{mires}
\framesubtitle{Results}

\bi
\item Restricting thresholds and loadings provides a good fit
  \bi \item We can compare the scale (variance) of the latent factors \ei
\item Models with restricted intercepts do \emph{not} pass MI test
  \bi
  \item Unclear whether mean comparisons can be done
  \item \cite{Wu2016} vs \cite{Millsap2004}
  \ei
% \item Might \emph{age differences} in the sample be playing a role?
%   \bi
%   \item BCS and MCS samples differ due to survey design \hyperlink{agehist}{\beamerbutton{Graph}}
%   \item But restricting the age range to maximise overlap does not give significantly different results \hyperlink{fit4}{\beamerbutton{Det.}}
%   \ei
  \pause
\item \textbf{Q1}: Can we derive comparable measures of noncognitive skills across cohorts?
\item Yes, we can use the model with non-invariant intercepts to score the latent factors (externalising and internalising skills)
\ei

@@

@@

\begin{frame}
\frametitle{Inequality}\label{meanci}
\framesubtitle{Visualising the gradient \hyperlink{loessext}{\beamerbutton{EXT}}\hyperlink{loessint}{\beamerbutton{INT}}}
\begin{figure}
<<FACINEQ, dev='tikz', fig.height=6.7, fig.width=10, out.width='\\linewidth'>>=
@
\end{figure}
\end{frame}

% \begin{frame}
% \frametitle{Inequality}
% \framesubtitle{Quantifying the gradient -- inflation- and growth-adjusted income}
% \centering
% \resizebox{!}{4cm}{%
% <<FA_REGS_REAL, dependson='FA_SCORES_SELECT', results='asis'>>=
% # regress scores on income
% library(dplyr)
% library(stargazer)
% 
% scores2plot$incq_real <- factor(ntile(scores2plot$faminc_real, 5))
% 
% # get min, max
% minmax.real <-aggregate(scores2plot[,c("faminc_real")],list(scores2plot$incq_real), 
%             FUN = function(x) c(min = min(x, na.rm=T), max = max(x, na.rm=T)))
% minmax.real <- round(minmax.real[,-1],2)*1000
% 
% r.ext.f.q <- lm(EXT ~ as.factor(incq_real)*cohort, data=subset(scores2plot, sex=="F"))
% r.int.f.q <- lm(INT ~ as.factor(incq_real)*cohort, data=subset(scores2plot, sex=="F"))
% 
% r.ext.m.q <- lm(EXT ~ as.factor(incq_real)*cohort, data=subset(scores2plot, sex=="M"))
% r.int.m.q <- lm(INT ~ as.factor(incq_real)*cohort, data=subset(scores2plot, sex=="M"))
% 
% stargazer(r.ext.m.q, r.int.m.q, r.ext.f.q, r.int.f.q,
%           column.labels=c("Males","Females"), column.separate=c(2,2),
%           dep.var.caption = "", multicolumn = FALSE,
%           omit=c("Constant"),
%           covariate.labels=c(
%                 paste0("Income Q2 [",toString(minmax.real[2,1]),"-",toString(minmax.real[2,2])," £/w]"),
%                 paste0("Income Q3 [",toString(minmax.real[3,1]),"-",toString(minmax.real[3,2])," £/w]"),
%                 paste0("Income Q4 [",toString(minmax.real[4,1]),"-",toString(minmax.real[4,2])," £/w]"),
%                 paste0("Income Q5 [",toString(minmax.real[5,1]),"+ £/w]"),
%                              "MCS dummy",
%                              "Income Q2 x MCS",
%                              "Income Q3 x MCS",
%                              "Income Q4 x MCS",
%                              "Income Q5 x MCS"
%                              ),
%           no.space=TRUE, 
%           omit.stat= c("rsq", "f", "ser", "aic", "ll"),
%           float=FALSE    # needs begin table outside it
% )
% @
% }
% \end{frame}

\begin{frame}
\frametitle{Inequality}
\framesubtitle{Quantifying the gradient}
\centering
\resizebox{12cm}{!}{%
<<FA_REGS_REAL_MF, dependson='FA_SCORES', results='asis'>>=
# regress scores on income
library(dplyr)
library(stargazer)

r.ext.m.bcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="BCS"))
r.ext.m.mcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="MCS"))
r.int.m.bcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="BCS"))
r.int.m.mcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="MCS"))

r.ext.f.bcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="BCS"))
r.ext.f.mcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="MCS"))
r.int.f.bcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="BCS"))
r.int.f.mcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="MCS"))

stargazer(r.ext.m.bcs, r.ext.m.mcs , r.int.m.bcs, r.int.m.mcs, r.ext.f.bcs, r.ext.f.mcs , r.int.f.bcs, r.int.f.mcs,
          column.labels=c("BCS M","MCS M","BCS M","MCS M","BCS F","MCS F","BCS F","MCS F"),
          dep.var.caption = "", multicolumn = FALSE,
          omit=c("Constant"),
          covariate.labels=c(
                             "Income Q2",
                             "Income Q3",
                             "Income Q4",
                             "Income Q5"
                             ),
          no.space=TRUE,
          omit.stat= c("rsq", "f", "ser", "aic", "ll"),
          float=FALSE    # needs begin table outside it
)
@
}
\end{frame}

% 
% \begin{frame}
% \frametitle{Inequality}
% \framesubtitle{Quantifying the gradient -- males}
% \centering
% \resizebox{12cm}{4cm}{%
% <<FA_REGS_REAL_M, dependson='FA_SCORES', results='asis'>>=
% # regress scores on income
% library(dplyr)
% library(stargazer)
% 
% 
% r.ext.m.bcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="BCS"))
% r.ext2.m.bcs <- lm(EXT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="M" & cohort=="BCS"))
% r.ext.m.mcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="MCS"))
% r.ext2.m.mcs <- lm(EXT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="M" & cohort=="MCS"))
% r.int.m.bcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="BCS"))
% r.int2.m.bcs <- lm(INT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="M" & cohort=="BCS"))
% r.int.m.mcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="M" & cohort=="MCS"))
% r.int2.m.mcs <- lm(INT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="M" & cohort=="MCS"))
% 
% stargazer(r.ext.m.bcs, r.ext2.m.bcs, r.int.m.bcs, r.int2.m.bcs, r.ext.m.mcs, r.ext2.m.mcs, r.int.m.mcs, r.int2.m.mcs,
%           column.labels=c("BCS","MCS"), column.separate=c(4,4),
%           dep.var.caption = "", multicolumn = FALSE,
%           omit=c("Constant"),
%           covariate.labels=c(
%                              "Income Q2",
%                              "Income Q3",
%                              "Income Q4",
%                              "Income Q5",
%                              "Birthweight",
%                              "Mat. Smoking in preg.",
%                              "Father years of schooling",
%                              "Mother years of schooling"
%                              ),
%           no.space=TRUE, 
%           omit.stat= c("rsq", "f", "ser", "aic", "ll"),
%           float=FALSE    # needs begin table outside it
% )
% @
% }
% \end{frame}
% 
% 
% 
% \begin{frame}
% \frametitle{Inequality}
% \framesubtitle{Quantifying the gradient -- females}
% \centering
% \resizebox{12cm}{4cm}{%
% <<FA_REGS_REAL_F, dependson='FA_SCORES', results='asis'>>=
% # regress scores on income
% library(dplyr)
% library(stargazer)
% 
% 
% r.ext.f.bcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="BCS"))
% r.ext2.f.bcs <- lm(EXT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="F" & cohort=="BCS"))
% r.ext.f.mcs <- lm(EXT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="MCS"))
% r.ext2.f.mcs <- lm(EXT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="F" & cohort=="MCS"))
% r.int.f.bcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="BCS"))
% r.int2.f.bcs <- lm(INT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="F" & cohort=="BCS"))
% r.int.f.mcs <- lm(INT ~ as.factor(incq), data=subset(scores2plot, sex=="F" & cohort=="MCS"))
% r.int2.f.mcs <- lm(INT ~ as.factor(incq) + bwt + as.factor(smkpr) + ysch_fath + ysch_moth, data=subset(scores2plot, sex=="F" & cohort=="MCS"))
% 
% 
% 
% stargazer(r.ext.f.bcs, r.ext2.f.bcs, r.int.f.bcs, r.int2.f.bcs, r.ext.f.mcs, r.ext2.f.mcs, r.int.f.mcs, r.int2.f.mcs,
%           column.labels=c("BCS","MCS"), column.separate=c(4,4),
%           dep.var.caption = "", multicolumn = FALSE,
%           omit=c("Constant"),
%           covariate.labels=c(
%                              "Income Q2",
%                              "Income Q3",
%                              "Income Q4",
%                              "Income Q5",
%                              "Birthweight",
%                              "Mat. Smoking in preg.",
%                              "Father years of schooling",
%                              "Mother years of schooling"
%                              ),
%           no.space=TRUE, 
%           omit.stat= c("rsq", "f", "ser", "aic", "ll"),
%           float=FALSE    # needs begin table outside it
% )
% @
% }
% \end{frame}

@@

% \begin{frame}
% \frametitle{Returns}
% \framesubtitle{Education returns to behaviour skills in BCS}
% \centering
% \resizebox{!}{4cm}{%
% <<FA_RETURNS, dependson='FA_SCORES_SELECT', results='asis'>>=
% # regress scores on income
% library(dplyr)
% library(stargazer)
% 
% # get BCS data and make dummy for higher education
% scoresBCS <- scores2plot[scores2plot$cohort=="BCS",]
% scoresBCS$highered <- as.numeric(scoresBCS$hinvq00>3)
% scoresBCS[is.na(scoresBCS$hinvq00), "highered"] <- NA
% 
% # females
% r.nvq.f <- list()
% r.nvq.f[[1]] <- lm(highered ~ EXT + INT, data=subset(scoresBCS, sex=="F"))
% r.nvq.f[[2]] <- lm(highered ~ EXT + INT + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="F"))
% r.nvq.f[[3]] <- lm(highered ~ EXT + INT + factor(incq), data=subset(scoresBCS, sex=="F"))
% r.nvq.f[[4]] <- lm(highered ~ EXT + INT + ysch_moth + ysch_fath, data=subset(scoresBCS, sex=="F"))
% r.nvq.f[[5]] <- lm(highered ~ EXT + INT + factor(incq) + ysch_moth + ysch_fath + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="F"))
% 
% # females
% r.nvq.m <- list()
% r.nvq.m[[1]] <- lm(highered ~ EXT + INT, data=subset(scoresBCS, sex=="M"))
% r.nvq.m[[2]] <- lm(highered ~ EXT + INT + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="M"))
% r.nvq.m[[3]] <- lm(highered ~ EXT + INT + factor(incq), data=subset(scoresBCS, sex=="M"))
% r.nvq.m[[4]] <- lm(highered ~ EXT + INT + ysch_moth + ysch_fath, data=subset(scoresBCS, sex=="M"))
% r.nvq.m[[5]] <- lm(highered ~ EXT + INT + factor(incq) + ysch_moth + ysch_fath + cog1 + cog2 + cog3, data=subset(scoresBCS, sex=="M"))
% 
% stargazer(r.nvq.m[[1]], r.nvq.m[[2]], r.nvq.m[[3]], r.nvq.m[[4]], r.nvq.m[[5]],
%           r.nvq.f[[1]], r.nvq.f[[2]], r.nvq.f[[3]], r.nvq.f[[4]], r.nvq.f[[5]],
%           dep.var.caption = "Completed Higher Ed. at 30",
%           column.labels=c("Males","Females"), column.separate=c(5,5),
%           omit=c("Constant"),
%           covariate.labels=c("Externalising skill at 5",
%                              "Internalising skill at 5",
%                              "EPVT Z at 5",
%                              "Human figure drawing Z at 5",
%                              "Copy design Z at 5",
%                              "Family inc. at 10 Q2",
%                              "Family inc. at 10 Q3",
%                              "Family inc. at 10 Q4",
%                              "Family inc. at 10 Q5",
%                              "Mother's years of schooling",
%                              "Father's years of schooling"
%                              ),
%           no.space=TRUE, 
%           omit.stat= c("rsq", "f", "ser", "aic", "ll"),
%           float=FALSE    # needs begin table outside it
% )
% @
% }
% \end{frame}

@@

@@

>>>>

<<READ, cache=FALSE >>=
library(here)
read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_scores.R"))
read_chunk(here("codes/R/4_scores_aux.R"))
read_chunk(here("codes/R/5_graphs.R"))
read_chunk(here("codes/R/6_selectvars.R"))
read_chunk(here("codes/R/8_regs.R"))
read_chunk(here("codes/R/getpars.R"))

@@

<<PREAMBLE >>=
@

@@

\date[TAPES]{Trans-Atlantic Public Economics Seminar \\ \today}

@@

\begin{frame}
\frametitle{Harmonisation}\label{meantab_f}
\framesubtitle{Choice of common items (females) \hyperlink{meantab_m}{\beamerbutton{Males}}}
\centering
\resizebox{!}{4cm}{
<<MEANTAB_F, dependson="MEANTABLE", results='asis'>>=
require(xtable)

table <- meantab[[2]] # females (but just need item names)
table <- table[,!names(table) %in% c("cats", "fac", "bcs.num", "mcs.num")] # drop if unneeded

@@

<<FA_INV_MAIN>>=
# main models only
@

<<FA_FIT>>=
# assemble fit indices into matrices
@

<<FA_SCORES_MAIN>>=
# produce scores for main models
@

<<FA_SCORES_BIND>>=
# bind scores with data
@

@@

\begin{frame}
\frametitle{Measurement Invariance}\label{mires}
\framesubtitle{Results \hyperlink{measpars}{\beamerbutton{Measurement}}\hyperlink{lvpars}{\beamerbutton{Latent variable}}}

\bi
\item Restricting thresholds and loadings provides a good fit \hyperlink{fit}{\beamerbutton{Fit}}
  \bi \item We can compare the scale (variance) of the latent factors \ei
\item Models with restricted intercepts do \emph{not} pass MI test
  \bi
  \item Unclear whether mean comparisons can be done
  \item \cite{Wu2016} vs \cite{Millsap2004}
  \ei
% \item Might \emph{age differences} in the sample be playing a role?
%   \bi
%   \item BCS and MCS samples differ due to survey design \hyperlink{agehist}{\beamerbutton{Graph}}
%   \item But restricting the age range to maximise overlap does not give significantly different results \hyperlink{fit4}{\beamerbutton{Det.}}
%   \ei
  \pause
\item \textbf{Q1}: Can we derive comparable measures of noncognitive skills across cohorts?
\item Yes, we can use the model with non-invariant intercepts to score the latent factors (externalising and internalising skills)
\ei

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% SCORES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Factor scores}\label{density}
\framesubtitle{Densities \hyperlink{rawhist}{\beamerbutton{Raw scores}}}
\begin{figure}
<<FACDENS, dependson="FA_SCORES_BIND", dev='tikz', fig.height=7.5, fig.width=10, out.width='.9\\linewidth'>>=
@
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Inequality}\label{ineq_uc}
\framesubtitle{Unconditional inequality}
\centering
<<INEQ_STATS, dependson="FA_SCORES_BIND", results='asis'>>=

# income 
tb <- data.frame(
  aggregate(scores2plot$faminc10_infl, by=list(scores2plot$cohort), FUN = function(x) quantile(x, c(.1, .25, .75, .9), na.rm=T))
)
tb$d9010 <- tb$x[,4]/tb$x[,1]
tb$d7525 <- tb$x[,3]/tb$x[,2]

tb.ext <- data.frame(
  aggregate(scores2plot$EXT, by=list(scores2plot$cohortsex), FUN = function(x) quantile(x, c(.1, .25, .5, .75, .9), na.rm=T))
)
tb.ext$d9010 <- abs(tb.ext$x[,"90%"]-tb.ext$x[,"10%"])
tb.ext$d7525 <- abs(tb.ext$x[,"75%"]-tb.ext$x[,"25%"])
tb.ext$d9050 <- abs(tb.ext$x[,"90%"]-tb.ext$x[,"50%"])
tb.ext$d5010 <- abs(tb.ext$x[,"50%"]-tb.ext$x[,"10%"])
rownames(tb.ext) <- tb.ext$Group.1
tb.ext <- t(tb.ext[,-c(1,2)]) # remove aggregated quantiles and transpose
tb.ext <- tb.ext[,c("BCS.M","MCS.M","BCS.F","MCS.F")]

tb.int <- data.frame(
  aggregate(scores2plot$INT, by=list(scores2plot$cohortsex), FUN = function(x) quantile(x, c(.1, .25, .5, .75, .9), na.rm=T))
)
tb.int$d9010 <- abs(tb.int$x[,"90%"]-tb.int$x[,"10%"])
tb.int$d7525 <- abs(tb.int$x[,"75%"]-tb.int$x[,"25%"])
tb.int$d9050 <- abs(tb.int$x[,"90%"]-tb.int$x[,"50%"])
tb.int$d5010 <- abs(tb.int$x[,"50%"]-tb.int$x[,"10%"])
rownames(tb.int) <- tb.int$Group.1
tb.int <- t(tb.int[,-c(1,2)]) # remove aggregated quantiles and transpose
tb.int <- tb.int[,c("BCS.M","MCS.M","BCS.F","MCS.F")]

# assemble and print
table <- rbind(tb.ext,tb.int)
table <- cbind(data.frame(as.matrix(rep(c("90-10", "75-25", "90-50", "50-10"),2))),
               table)

print(xtable(table,
                    align="L{0cm}L{.15\\textwidth}C{.1\\textwidth}C{.1\\textwidth}C{.1\\textwidth}C{.1\\textwidth}",
                    digits = 4
                    ),
             size="\\scriptsize",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0,4)),
                              command = c(
                              # header
            "Measure & \\multicolumn{2}{c}{\\textbf{Males}} & \\multicolumn{2}{c}{\\textbf{Females}} \\\\ \\cmidrule(lr){2-3}  \\cmidrule(lr){4-5} 
                       & BCS & MCS & BCS & MCS  \\\\
                      \\textbf{Externalising} \\\\ ",
                      "\\textbf{Internalising} \\\\ \\midrule "
                                    )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabular", width = "\\textwidth",
             floating = FALSE
)

@
\end{frame}

<<FACINEQ_MAKE>>=
# make factor inequality graphs
@

\begin{frame}
\frametitle{Inequality}\label{ineq_sc}
\framesubtitle{Social class}
\vspace{-.2cm}
\begin{figure}
<<FACINEQ_SC, dependson="FA_SCORES_BIND", dev='tikz', fig.height=7.5, fig.width=10, out.width='.9\\linewidth'>>=
# plot
fi <- fi_sc # select result
gridExtra::grid.arrange(fi$ineqlist[[1]],fi$ineqlist[[2]], 
                        fi$ineqlist[[3]],fi$ineqlist[[4]],
                        fi$histlist[[1]],fi$histlist[[2]], fi$legend,
                        ncol=2, nrow=4, heights = c(4,4,2,0.5))
@
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Inequality}\label{ineq_sc}
\framesubtitle{Age mother left education}
\vspace{-.2cm}
\begin{figure}
<<FACINEQ_YS, dependson="FA_SCORES_BIND", dev='tikz', fig.height=7.5, fig.width=10, out.width='.9\\linewidth'>>=
# plot
fi <- fi_ys # select result
gridExtra::grid.arrange(fi$ineqlist[[1]],fi$ineqlist[[2]], 
                        fi$ineqlist[[3]],fi$ineqlist[[4]],
                        fi$histlist[[1]],fi$histlist[[2]], fi$legend,
                        ncol=2, nrow=4, heights = c(4,4,2,0.5))
@
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Inequality}\label{ineq_sc}
\framesubtitle{Maternal education and employment}
\vspace{-.2cm}
\begin{figure}
<<FACINEQ_MECS, dependson="FA_SCORES_BIND", dev='tikz', fig.height=8.5, fig.width=13.5, out.width='\\linewidth'>>=
# plot
fi <- fi_mecs # select result
gridExtra::grid.arrange(fi$ineqlist[[1]],fi$ineqlist[[2]], 
                        fi$ineqlist[[3]],fi$ineqlist[[4]],
                        fi$histlist[[1]],fi$histlist[[2]], fi$legend,
                        ncol=2, nrow=4, heights = c(4,4,2,0.5))
@
\end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% EXPLAINING EXT and INT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<SELECTVARS>>=
# define variables and formulas for regression and decomposition
@

<<REGS_DEP, dependson="SELECTVARS">>=
# run regressions explaining EXT INT
@

\begin{frame}
\frametitle{What explains behavioural skills?}

write about variables used and groups

\begin{frame}
\frametitle{What explains behavioural skills?}
\framesubtitle{Males}
\begin{table}
\centering
\resizebox{!}{4cm}{
<<REGS_M, results='asis', dependson="REGRESSIONS">>=

# select models
regs <- list(r_ext$BCS.M[["OLS"]],r_ext$MCS.M[["OLS"]],r_int$BCS.M[["OLS"]],r_int$MCS.M[["OLS"]])

# robust SEs
robust_se <- list()
robust_p  <- list()
for (i in 1:length(regs)) {
  cov1              <- sandwich::vcovHC(regs[[i]], type = "HC1")
  ct                <- lmtest::coeftest(regs[[i]], vcov = cov1)
  robust_se[[i]] <- ct[, 2]
  robust_p[[i]] <- ct[, 4]
}

texreg::texreg(regs,
               stars = c(0.1, 0.05, 0.01), digits = 3,
               override.se = robust_se, override.pvalues = robust_p,
               single.row = TRUE, scriptsize = TRUE,
               caption = "", label = "",
               omit.coef = "region|Inter",
               groups = grouplabs,
               custom.coef.names = varlabs,
               custom.model.names = c("EXT BCS", "EXT MCS", "INT BCS", "INT MCS"),
               table = FALSE
               )

@
}
\end{table}
\end{frame}

\begin{frame}
\frametitle{What explains behavioural skills?}
\framesubtitle{Females}
\begin{table}
\centering
\resizebox{!}{4cm}{
<<REGS_F, results='asis', dependson="REGRESSIONS">>=

# select models
regs <- list(r_ext$BCS.F[["OLS"]],r_ext$MCS.F[["OLS"]],r_int$BCS.F[["OLS"]],r_int$MCS.F[["OLS"]])

# robust SEs
robust_se <- list()
robust_p  <- list()
for (i in 1:length(regs)) {
  cov1              <- sandwich::vcovHC(regs[[i]], type = "HC1")
  ct                <- lmtest::coeftest(regs[[i]], vcov = cov1)
  robust_se[[i]] <- ct[, 2]
  robust_p[[i]] <- ct[, 4]
}

texreg::texreg(regs,
               stars = c(0.1, 0.05, 0.01), digits = 3,
               override.se = robust_se, override.pvalues = robust_p,
               single.row = TRUE, scriptsize = TRUE,
               caption = "", label = "",
               omit.coef = "region|Inter",
               groups = grouplabs,
               custom.coef.names = varlabs,
               custom.model.names = c("EXT BCS", "EXT MCS", "INT BCS", "INT MCS"),
               table = FALSE
               )

@
}
\end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% GELBACH DECOMPOSITION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
\frametitle{Decomposition (EXT)}
\framesubtitle{Explaining the education gradient}
\centering
\scriptsize
\resizebox{\textwidth}{!}{
\input{../../../tables/med_gelb_ext}
}
\end{frame}

\begin{frame}
\frametitle{Decomposition (INT)}
\framesubtitle{Explaining the education gradient}
\centering
\scriptsize
\resizebox{\textwidth}{!}{
\input{../../../tables/med_gelb_int}
}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%% EFFECTS ON LATER OUTCOMES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

<<REGS_OUTC, dependson="SELECTVARS">>=
# run regressions explaining adult outcomes
@

<<REGS_OUTC_TAB, dependson="REGS_OUTC">>=
# make tables
@

\begin{frame}
\frametitle{Outcomes}
\framesubtitle{Adolescence (BCS)}
\centering
\resizebox{\textwidth}{!}{
<<REGS_OUTC_BCS1, results='asis', dependson="REGRESSIONS">>=

# collapse to matrix (first 4 elements of bcs_outctab are adolescence)
bcs_outctab_mat <- do.call(rbind,lapply(bcs_outctab[c(1:4)],matrix,ncol=11,byrow=FALSE))
table <- bcs_outctab_mat

print(xtable(table,
                    align="R{0cm}L{.22\\textwidth}C{.05\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.05\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}",
                    digits = 3
                    ),
             size="\\scriptsize",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0)),
                              command = c(
                              # header
            " & \\multicolumn{5}{c}{\\textbf{Males}} & \\multicolumn{5}{c}{\\textbf{Females}} \\\\ \\cmidrule(lr){2-6}  \\cmidrule(lr){7-11}
& Mean & \\multicolumn{4}{c}{Coefficients} & Mean & \\multicolumn{4}{c}{Coefficients} \\\\ \\cmidrule(lr){3-6}  \\cmidrule(lr){8-11}"
            )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabular", width = "\\textwidth",
             floating = FALSE
)
@
}
\end{frame}

\begin{frame}
\frametitle{Outcomes}
\framesubtitle{Adulthood (BCS)}
\centering
\resizebox{\textwidth}{!}{
<<REGS_OUTC_BCS2, results='asis', dependson="REGRESSIONS">>=

# collapse to matrix (last 4 elements of bcs_outctab are adulthood)
bcs_outctab_mat <- do.call(rbind,lapply(bcs_outctab[c(5:8)],matrix,ncol=11,byrow=FALSE))
table <- bcs_outctab_mat

print(xtable(table,
                    align="R{0cm}L{.22\\textwidth}C{.05\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.05\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}",
                    digits = 3
                    ),
             size="\\scriptsize",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0)),
                              command = c(
                              # header
            " & \\multicolumn{5}{c}{\\textbf{Males}} & \\multicolumn{5}{c}{\\textbf{Females}} \\\\ \\cmidrule(lr){2-6}  \\cmidrule(lr){7-11}
& Mean & \\multicolumn{4}{c}{Coefficients} & Mean & \\multicolumn{4}{c}{Coefficients} \\\\ \\cmidrule(lr){3-6}  \\cmidrule(lr){8-11}"
            )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabular", width = "\\textwidth",
             floating = FALSE
)
@
}
\end{frame}

\begin{frame}
\frametitle{Outcomes}
\framesubtitle{Adolescence (MCS)}
\centering
\resizebox{\textwidth}{!}{
<<REGS_OUTC_MCS, results='asis', dependson="REGRESSIONS">>=

# collapse to matrix
mcs_outctab_mat <- do.call(rbind,lapply(mcs_outctab,matrix,ncol=11,byrow=FALSE))
table <- mcs_outctab_mat

print(xtable(table,
                    align="R{0cm}L{.22\\textwidth}C{.05\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.05\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}C{.075\\textwidth}",
                    digits = 3
                    ),
             size="\\scriptsize",
             include.rownames=F,
             include.colnames=F,
             booktabs = T,
             add.to.row = list(pos = c(list(0)),
                              command = c(
                              # header
            " & \\multicolumn{5}{c}{\\textbf{Males}} & \\multicolumn{5}{c}{\\textbf{Females}} \\\\ \\cmidrule(lr){2-6}  \\cmidrule(lr){7-11}
& Mean & \\multicolumn{4}{c}{Coefficients} & Mean & \\multicolumn{4}{c}{Coefficients} \\\\ \\cmidrule(lr){3-6}  \\cmidrule(lr){8-11}"
            )),
             sanitize.text.function = function(x){x},
             sanitize.rownames.function = function(x){""}, # to not print row numbers
             tabular.environment = "tabular", width = "\\textwidth",
             floating = FALSE
)
@
}
\end{frame}

@@

@@

\begin{frame}
\frametitle{Harmonisation}\label{meantab_m}
\framesubtitle{Choice of common items (males) \hyperlink{meantab_f}{\beamerreturnbutton{Females}}}
\centering
\resizebox{!}{4cm}{
<<MEANTAB_M, dependson="MEANTABLE", results='asis'>>=
require(xtable)

table <- meantab[[1]] # males
table <- table[,!names(table) %in% c("cats", "fac", "bcs.num", "mcs.num")] # drop if unneeded

@@

\begin{frame}
\frametitle{Factor scores}\label{rawhist}
\framesubtitle{Raw scores \hyperlink{density}{\beamerreturnbutton{Back}}}
\begin{figure}
<<RAWHIST, dependson="FA_SCORES_BIND", dev='tikz', fig.height=7.5, fig.width=10, out.width='.9\\linewidth'>>=
@
\end{figure}
\end{frame}
